Select-based random access to variable-byte encodings

### 2020-03-22 gradu/msc_english_contents.tex
subarray results

>>>>

\begin{figure}[ht]
\centering
\begin{tikzpicture}
\begin{axis}[
    xlabel={average integer byte length},
    ylabel={ms per million queries},
    xmin=1, xmax=8,
    ymin=0, ymax=4000,
    xtick={1,2,3,4,5,6,7,8},
    ytick={0,500,1000,1500,2000,2500,3000,3500,4000},
    legend pos=north west,
    ymajorgrids=true,
    grid style=dashed,
]

\addplot[
color=blue,
mark=square,
]
coordinates {
(1,394.90)(2,654.60)(3,976.20)(4,1282.50)(5,1711.70)(6,2256.70)(7,2954.30)(8,3326.50)
};
\addplot[
color=red,
mark=ball,
]
coordinates {
(1,776.70)(2,1484.30)(3,2246.60)(4,2570.30)(5,3476.20)(6,4144.80)(7,4760.40)(8,6771.50)
};
\addplot[
color=green,
mark=triangle,
]
coordinates {
(1,393.70)(2,732.00)(3,1087.70)(4,1445.50)(5,1893.60)(6,2423.50)(7,3133.10)(8,3612.80)
};
\addplot[
color=black,
mark=diamond,
]
coordinates {
(1,804.10)(2,1711.80)(3,2640.60)(4,3080.70)(5,4126.30)(6,5022.10)(7,5788.50)(8,8258.20)
};
\addplot[
color=orange,
mark=square*,
]
coordinates {
(1,422.00)(2,508.40)(3,547.90)(4,636.30)(5,645.60)(6,664.50)(7,683.70)(8,703.30)
};
\addplot[
color=blue,
mark=star,
]
coordinates {
(1,569.40)(2,694.80)(3,676.80)(4,691.70)(5,708.30)(6,716.50)(7,780.10)(8,812.20)
};
\legend{bris8, bris4, bris8v5, bris4v5, select8, select4 }

TODO: create a dataset with low numbers and some large ones (every 40th or so)

 - compare and explain

\end{axis}
\end{tikzpicture}
\caption{Rank and select performances with subarray fetching} \label{graph:subarray}
\end{figure}
